Fire Damage in Toronto: A Study of Contributing Factors

### 2024-09-27 paper/paper.qmd
coined a better title

---
title: "The Causes of Damage in Toronto Fire Incidents"
author: 
  - David Qi
thanks: "Code and data are available at: https://github.com/UTDQi/Fire_Incidents"
date: today
date-format: long
abstract: "This paper discusses some basic findings around the monetary and lives loss in Toronto fire incidents. By using data from open data Toronto and choosing the relevant entries, we have identified possible factors that influences monetary and lives loss in fire incidents. We identified unattended ignition sources as a significant risk factor for civilian casualties, highlighting the need for public awareness campaigns to educate communities about these potential hazards. Interestingly, we observed that increasing the number of responding personnel beyond 90 led to a reduction in civilian casualties, which contrasts with our initial expectations."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Fire Damage in Toronto: A Study of Contributing Factors"
author: 
  - David Qi
thanks: "Code and data are available at: https://github.com/UTDQi/Fire_Incidents"
date: today
date-format: long
abstract: "This paper discusses some basic findings around the monetary and lives loss in Toronto fire incidents. By using data from open data Toronto and choosing the relevant entries, we have identified possible factors that influences monetary and lives loss in fire incidents. We identified unattended ignition sources as a significant risk factor for civilian casualties, highlighting the need for public awareness campaigns to educate communities about these potential hazards. Interestingly, we observed that increasing the number of responding personnel beyond 90 led to a reduction in civilian casualties, which contrasts with our initial expectations."
format: pdf
number-sections: true
bibliography: references.bib
---
